---
title: "Meka Mccammon Excercise 7"
output:
  html_document:
    df_print: paged
date: "28 March 2020"
---

This notebook contains a demonstration of the use of a user defiend function to analyze professors' salaries 


## 1.
### *Create a function that accepts (1) a quantitative response variable, (2) a quantitative explanatory variable, and (3) a number. Suppose we denote the response variable as y, the explanatory variable as x, and the number as p. Your function should model y as a linear function of x and then for each (x,y) pair determine if the residual is one of the p largest in the set of the residuals, with lagest defined in terms of the absolute value (i.e. a residual of -10 is just as large as a residual of 10). The function should return a logical vector indicating TRUE for each pair that has one of the pth largest residuals and FALSE otherwise.*

x = explanatory variable,
y = response variable,
p = a number

```{r}
regress.residuals <-function(x, y, p) {
  res.model <- lm(y~x)
  abs.res <- abs(res.model$residuals)
  sort.res <- sort(abs.res$residuals, decreasing = TRUE)
  cutoff <- sort.res[p]
  logical.res <- (abs.res >= cutoff)
  return(logical.res)
}
```

## 2.
### *Obtain a real data set with quantitative response and explanatory variables (n>=50). Plot these on a scatterplot with a regression line. Use your function to help you highlight the 10% largest residuals on the scatterplot.*

```{r echo=FALSE}
library(here)
professor <- read.csv(here("Data","Salaries.csv"))

#10% of the largest residuals
p <- round(0.1*(nrow(professor)))

#Linear Regression Model
model <-regress.residuals(professor$salary, professor$yrs.since.phd, 20)

#Correlation
cor <- cor(professor$salary, professor$yrs.since.phd)

#Determine which residuals are largest 
residuals <- lm(professor$salary ~ professor$yrs.since.phd)
residuals

```



### The relationship of years since obtaining a PhD and salary 
```{r echo=FALSE}
plot(professor$salary, professor$yrs.since.phd,
     main = "Relationship between Years Since Obtaining a PhD and Salary",
     xlab = "Years Since PhD",
     ylab = "Salary",
     col = ifelse(model == TRUE, "purple","black"),
     pch = ifelse(model == TRUE, 15, 0))

abline(residuals)
```
